exploratory

### 2021-10-27 code/analysis_code/exploratory.Rmd
more processing

```{r}
library(ggplot2)
library(tidyverse)
library("readxl")
library(here)
```

@@

#percentage of male and female
```{r}
data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#number of people for each educational category
```{r}
table(data1$`Highest educational level`)
```
```{r}
sum(data1$'Highest educational level' == 'Primary')
sum(data1$'Highest educational level' == 'Secondary')
sum(data1$'Highest educational level' == 'University Postgraduate degree holder')
sum(data1$'Highest educational level' == 'University Undergraduate degree holder')
```
#percentage of people for each student category
```{r}
data1 %>% 
     group_by( `Highest educational level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#student/worker in the heathcare sector?
```{r}
table(data1$`Are you a student or worker in the healthcare sector?`)
```
#percentage of student/health worker

```{r}
data1 %>% 
     group_by( `Are you a student or worker in the healthcare sector?` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

#household members?
```{r}
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 60 years and above`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 18 to 59 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 12 to 17 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: Less than 12 years`)
```
```{r}
table(data1$`Which of the following categories best describes your current socio-economic situation?`)
```
```{r}
sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'High income category')
sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Low income category')
sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Lower middle income category')
sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Upper middle income category ')
```

#percentage of income category?
```{r}
data1 %>% 
     group_by( `Which of the following categories best describes your current socio-economic situation?` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
```{r}
table(data1$`Do you live in:`)
```
```{r}
sum(data1$'Do you live in:' == 'A rural place / village')
sum(data1$'Do you live in:' == 'A Sub-urban setting / urban slum')
sum(data1$'Do you live in:' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
data1 %>% 
     group_by( `Do you live in:` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
```{r}
table(data1$`Which source of COVID-19 information/advice do you trust the most?`)
```
#most trusted source?
```{r}
data1 %>% 
     group_by( `Which source of COVID-19 information/advice do you trust the most?` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'No')
sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'Yes')
```

#percentage of work from home or not?
```{r}
data1 %>% 
     group_by( `Are you currently working/studying from home because of the COVID-19 outbreak?` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#Descriptive analysis for each question?
```{r}
table(data1$`Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`)
```
```{r}
table(data1$`Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`)
```
#correct knowledge of their status
```{r}
data1 %>% 
     group_by( `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`)
```
#worried about re-infection
```{r}
data1 %>% 
     group_by( `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

>>>>

```{r}
library(ggplot2)
library(tidyverse)
library("readxl")
library(dplyr)
library(here)
```

@@

#percentage of male and female
```{r}
data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#number of people for each educational category
```{r}
table(data1$`education`)
```
```{r}
sum(data1$'education' == 'Primary')
sum(data1$'education' == 'Secondary')
sum(data1$'education' == 'University Postgraduate degree holder')
sum(data1$'education' == 'University Undergraduate degree holder')
```
#percentage of people for each student category
```{r}
data1 %>% 
     group_by( `education` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#student/worker in the heathcare sector?
```{r}
table(data1$`student/heathworker`)
```

#percentage of student/health worker

```{r}
data1 %>% 
     group_by( `student/heathworker` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

#household members?
```{r}
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 60 years and above`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 18 to 59 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 12 to 17 years`)
table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: Less than 12 years`)
```
```{r}
table(data1$`economic_status`)
```
```{r}
sum(data1$'economic_status' == 'High income category')
sum(data1$'economic_status' == 'Low income category')
sum(data1$'economic_status' == 'Lower middle income category')
sum(data1$'economic_status' == 'Upper middle income category ')
```

#percentage of income category?
```{r}
data1 %>% 
     group_by( `economic_status` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
```{r}
table(data1$`residence`)
```
```{r}
sum(data1$'residence' == 'A rural place / village')
sum(data1$'residence' == 'A Sub-urban setting / urban slum')
sum(data1$'residence' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
data1 %>% 
     group_by( `residence` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`trusted_source`)
```
#most trusted source?
```{r}
data1 %>% 
     group_by( `trusted_source` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
sum(data1$'work_from_home' == 'No')
sum(data1$'work_from_home' == 'Yes')
```

#percentage of work from home or not?
```{r}
data1 %>% 
     group_by( `work_from_home` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#Descriptive analysis for each question?
```{r}
table(data1$`quarantined_or_not`)
```
#Quarantined or not
```{r}
data1 %>% 
     group_by( `quarantined_or_not` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`infection_status_info`)
```
#correct knowledge of their status
```{r}
data1 %>% 
     group_by( `infection_status_info` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`worry_level`)
```
#worried about re-infection
```{r}
data1 %>% 
     group_by( `worry_level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
